The Privacy of Private Browsing

### 2013-12-16 finalproject/paper.tex
regenerated paper

\begin{document}
  \singlespacing
  \title{The Privacy of Private Browsing}
  \author{Ashley Hedberg\thanks{\emph{Mentor:} Ming Chow, Tufts University} \\
  \href{mailto:ashley.hedberg@tufts.edu}{ashley.hedberg@tufts.edu}}
  \date{}
  \maketitle

  \begin{abstract}
  Most modern web browsers have a ``private browsing'' mode that supposedly 
  allows a user to surf the internet without leaving any traces of his or her
  activity on his or her machine. However, the notion of ``private browsing'' 
  offers users a false sense of security, as browsing information is often left
  behind when a private browsing session terminates. Several researchers have 
  already demonstrated methods of detecting this information. These include the
  analysis of the hard drive, memory, and the pagefile on Windows machines.
  The existence of private browsing artifacts on a user’s machine raises many 
  questions: how much privacy do web browser developers actually aim to provide
  with ``private browsing'' modes? Are these goals accurately conveyed to the 
  end user? And, if the user’s browsing session can be reconstructed from these 
  artifacts, how much information would digital forensics professionals be 
  able to gain? This paper seeks to answer these questions and to prove that 
  such artifactscan be used to determine, at least in part, what a user was 
  doing during his or her ``private browsing'' session---thereby rendering it 
  not very private at all.
  \end{abstract}

@@

    \subsection{Firefox}
    In 2011, researchers discovered that Firefox 3.6.11 stored browser history
    and search engine keywords in the computer's physical memory and that this
    information could be accessed after the browsing session was terminated.
    An analysis of the contents of pagefile.sys revealed similar information.
    \cite{said11} The presence of these in-memory artifacts persisted through 
    Firefox 17.0.1.\cite{ohana13} Additionally, digital certificates received 
    during private browsing sessions in Firefox 3.6 were not removed from their 
    on-disk database once the browsing session was terminated.\cite{aggarwal10}

@@

    \subsection{Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13} Internet Explorer 8.0.6001.18702
    continued to cache web pages on the hard drive during an InPrivate
    Browsing session, but these files were deleted once the browser window was
    closed. This means that fragments of these files---and thus a record of the
    user's browsing history---could be discovered by analyzing the free and
    slack space of the hard drive.\cite{said11} Login information for email
    accounts and full image artifacts were discovered on the machine after an 
    InPrivate Browsing session using Internet Explorer 8.0 as recently as 2013.
    \cite{ohana13} Researchers recently determined that Internet Explorer log 
    files no longer contained evidence of browsing history as of version 
    10.0.9200.16521. This had been an issue in previous versions of the 
    browser.\cite{satvat13}

>>>>

\begin{document}
  \title{The Privacy of Private Browsing}
  \author{Ashley Hedberg\thanks{\emph{Mentor:} Ming Chow, Tufts University} \\
  \href{mailto:ashley.hedberg@tufts.edu}{ashley.hedberg@tufts.edu}}
  \date{}
  \maketitle

  \begin{abstract}
  Most modern web browsers have a ``private browsing'' mode that supposedly 
  allows a user to surf the internet without leaving any traces of his or her
  activity on his or her machine. However, the notion of ``private browsing'' 
  offers users a false sense of security, as browsing information is often left
  behind when a private browsing session terminates. Several researchers have 
  already demonstrated methods of detecting this information. These include the
  analysis of the hard drive, memory, and the pagefile on Windows machines.
  The existence of private browsing artifacts on a user's machine raises many 
  questions: how much privacy do web browser developers actually aim to provide
  with ``private browsing'' modes? Are these goals accurately conveyed to the 
  end user? And, if the user’s browsing session can be reconstructed from these 
  artifacts, how much information would digital forensics professionals be 
  able to gain? This paper seeks to answer these questions and to prove that 
  such artifacts can be used to determine, at least in part, what a user was 
  doing during his or her ``private browsing'' session---thereby rendering it 
  not very private at all.
  \end{abstract}

@@

    \subsection{Mozilla Firefox}
    In 2011, researchers discovered that Firefox 3.6.11 stored browser history
    and search engine keywords in the computer's physical memory and that this
    information could be accessed after the browsing session was terminated.
    An analysis of the contents of pagefile.sys revealed similar information.
    \cite{said11} The presence of these in-memory artifacts persisted through 
    Firefox 17.0.1.\cite{ohana13} Additionally, digital certificates received 
    during private browsing sessions in Firefox 3.6 were not removed from their 
    on-disk database once the browsing session was terminated.\cite{aggarwal10}

@@

    \subsection{Microsoft Internet Explorer}
    Internet Explorer leaves the most artifacts behind when its InPrivate
    Browsing mode terminates.\cite{ohana13} Internet Explorer 8.0.6001.18702
    continued to cache web pages on the hard drive during an InPrivate
    Browsing session, but these files were deleted once the browser window was
    closed. This means that fragments of these files---and thus a record of the
    user's browsing history---could be discovered by analyzing the free and
    slack space of the hard drive.\cite{said11} Login information for email
    accounts and full image artifacts were discovered on the machine after an 
    InPrivate Browsing session using Internet Explorer 8.0 as recently as 2013.
    \cite{ohana13} Researchers recently determined that Internet Explorer log 
    files no longer contained evidence of browsing history as of version 
    10.0.9200.16521. This had been an issue in previous versions of the 
    browser.\cite{satvat13}
